Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-25 paper/paper.tex
pass on V.B

We used the official conformance test suite
Test262~\cite{ecma262-conformance-suite} to evaluate conformance of
engines to the \js\ current standard. As it is acceptable to release
engines fulfilling the specification only partially~\cite{kangax}, it
is expected that engines do not fully pass this test. However, we
expect that results provide indication of engine's maturity. In the
\begin{wraptable}[10]{r}{0.25\textwidth}
%  \vspace{-3ex}
  \centering
  \caption{\label{tab:test262}Percentage of passing tests on
    the Test262 conformance suite.}
  \small
  \begin{tabular}{crr}
    \toprule
    engine & \% passing \\
    \midrule
    \jsc{} & 92\%\\
    \veight{} & 95\% \\
    \chakra{} & 75\% \\    
    \smonkey{} & 93\% \\
    \bottomrule
  \end{tabular}
  \normalsize
  \vspace{-3ex}  
\end{wraptable}
limit, it is not desirable to flood bug reports on engines at early
stages of development. We ran the suite once a day for seven
consecutive days from the period of 16 to 22 of August,
2018. Table~\ref{tab:test262} shows the average number of passing
tests over this period. The variance of results was negligible; for
that reasons, we omited standard deviations. We noticed that all four
engines we analyzed but \chakra{} use some variant of the Test262
suite as part of their regression process, but we used the same
version in this experiment; the one available from the Test262 web
site~\cite{ecma262-conformance-suite}. Results show that there are
still many unsupported cases as can be observed from the percentages
in the table, but the number of passing tests is high, with
\veight\ and \smonkey\ performing better compared to others and
\chakra\ performing well worse than others. It is important to
highlight that failures in this conformance test suite indicates
missing features as opposed to bugs. However, note that \chakra\ is
both the engine that has the lowest passing ratio in the conformance
test suite and the one we were able to find more bugs. Although it is
possible to find correlation between the percentage of passing tests
in the conformance suite (as per Table~\ref{tab:test262}) and reliability as
measured by the number of bugs found (as per
Figure~\ref{fig:summary}), we do not not imply causality.

@@

%% This suggests that the investiment in
%% testing paid off in this case.
\begin{table}[h]
  \centering
  \caption{\label{tab:cross-testing}Number of failures observed exchanging
  test suites.}
  \begin{tabular}{crrrr}
    \toprule
    test suite\textbackslash{}engine & \jsc{} & \veight{} & \smonkey{} & \chakra{}\\
    \midrule
    % \Fix{Versions (03.08)} & 234555 & 7.0.158 & 62.0b14 & 1.10.1 \\
    \Comment{
      Lembrar dos testes que os testes da propria engine falham:
      V8 0 
      JSC 2 
      Spidermonkey 58
    }
    \jsc{} & - & 9 & 10 & 58   \\
    \veight{} & 29 & - & 0 & 0  \\
%    \chakra{} & - & - & - & -  \\
    \smonkey{} & 217 & 106 & - & 278 \\
    Duktape & 0 & 4 & 4 & 1   \\
    \jerry{} & 23 & 25 & 22 & 23   \\
    JSI & 0 & 0 & 0 & 0   \\ 
   Tiny-js & 0 & 0 & 0 & 0  \\
    \midrule
   \textbf{total} & 270 & 145 & 36 & 361 \\
    \bottomrule 
  \end{tabular}
\end{table}

@@

@@

Table~\ref{fig:piecharts-transplantation} shows the distribution of
false and true positives. Considering false positives, ``Undefined
Behavior'' and ``Non-Standard Element'' were the most predominant
sources. Considering true positives, we found a reasonable number of
duplicate reports, but not enough high to justify attempting to
automate the detection of duplicates.
Table~\ref{tab:test-transplantation-bugs} lists all bugs we found with
test transplantation. The first column shows the identifier we
assigned to the bug\Comment{, column ``Date'' shows the date the bug
  was reported in the format ``m/dd'',} column ``Engine'' shows the
affected engine, column ``Status'' indicates the status of the bug
report at the time of the writing (\eg{},``New'', ``Rejected'',
``Confirmed'', ``Fixed''). The status string appear in bold face for
status ``Confirmed'' or higher (\ie{}, ``Assigned'' or ``Fixed'').
Column ``Url'' shows the URL (de-anonymized upon request) for the bug report entry in the
corresponding bug-tracking system, column ``Severity''
shows the severity level for confirmed bugs, and, finally, column
``Suite'' shows the name of the engine that originated the
test. Note that bug reports \#4 and \#23 afected multiple engines.

Considering severity levels, it is important to note that \jsc{}
uses five levels~\cite{jsc-severity} whereas
\chakra{}~\cite{chakra-severity} and
\smonkey{}~\cite{mozilla-severity} use only two. As usual, the
smallest the severity value the highest the severity of the bug. We
use a dash (``-'') as the severity level for bugs with pending
confirmation.  No bug we reported in this experiment was rejected.  Of
the \Fix{17} bugs we reported in this experiment, \Fix{9} were
analyzed and moved from the status ``New'' to ``Confirmed''. Of these,
\Fix{8} are severity-2 bugs.  Although we did not find any showstopper
critical bugs, most of the bugs are seemingly important as per the
categorization given by engineers. Analyzing the issue tracker of
\chakra, we found that severity-1 bugs are rare. Considering the bugs
confirmed by developers, \chakra{} was the engine with the highest
number, \Fix{8} in total, with \Fix{1} bug fixed. Considering the
remaining engines, \veight{} developers confirmed \Fix{one} bug we
reported. Curiously, Google engineers confirmed that report in a few
hours. We found that development teams of other engines, specially
\jsc\, took much longer to analyze bug reports as can be observed by
some pending reports from April 2018.

Overall, we found these results promising given that precision (\ie{},
the ratio of true positives over all reports) needs to take into
account the cost of inspecting the failure~\cite{harman-ohearn-2018};
it took a week for the developer to inspect the entire set of
failures. The precision for \jsc\ was \Fix{X\%} (\ie, XX/270), which
seems a low rate, but it took approximately \Fix{x} days to find
\Fix{y} real bugs on this engine. Section~\ref{sec:bugs} shows samples
of false and true positives.

\begin{center}
  \fbox{
    \begin{minipage}{8cm}
      \textit{Summary:}~Test transplantation is effective at finding
      functional bugs. Although the inspection cost is non-negligible,
      the approach was able to reveal several bugs in widely popular
      engines.
      \end{minipage}
    }
\end{center}

>>>>

\begin{wraptable}[10]{r}{0.25\textwidth}
%  \vspace{-3ex}
  \centering
  \caption{\label{tab:test262}Percentage of passing tests on
    the Test262 conformance suite.}
  \small
  \begin{tabular}{crr}
    \toprule
    engine & \% passing \\
    \midrule
    \jsc{} & 92\%\\
    \veight{} & 95\% \\
    \chakra{} & 75\% \\    
    \smonkey{} & 93\% \\
    \bottomrule
  \end{tabular}
  \normalsize
\end{wraptable}
We used the official conformance test suite
Test262~\cite{ecma262-conformance-suite} to evaluate conformance of
engines to the \js\ current standard. As it is acceptable to release
engines fulfilling the specification only partially~\cite{kangax}, it
is expected that engines do not fully pass this test. However, we
expect that results provide indication of engine's maturity. In the
limit, it is not desirable to flood bug reports on engines at early
stages of development. We ran the suite once a day for seven
consecutive days from the period of 16 to 22 of August,
2018. Table~\ref{tab:test262} shows the average number of passing
tests over this period. The variance of results was negligible; for
that reasons, we omited standard deviations. We noticed that all four
engines we analyzed but \chakra{} use some variant of the Test262
suite as part of their regression process, but we used the same
version in this experiment; the one available from the Test262 web
site~\cite{ecma262-conformance-suite}. Results show that there are
still many unsupported cases as can be observed from the percentages
in the table, but the number of passing tests is high, with
\veight\ and \smonkey\ performing better compared to others and
\chakra\ performing well worse than others. It is important to
highlight that failures in this conformance test suite indicates
missing features as opposed to bugs. However, note that \chakra\ is
both the engine that has the lowest passing ratio in the conformance
test suite and the one we were able to find more bugs. Although it is
possible to find correlation between the percentage of passing tests
in the conformance suite (as per Table~\ref{tab:test262}) and reliability as
measured by the number of bugs found (as per
Figure~\ref{fig:summary}), we do not not imply causality.

@@

%% This suggests that the investiment in
%% testing paid off in this case.
\begin{table}[t]
  \centering
  \caption{\label{tab:cross-testing}Number of failures observed exchanging
  test suites.}
  \begin{tabular}{crrrr}
    \toprule
    test suite\textbackslash{}engine & \jsc{} & \veight{} & \smonkey{} & \chakra{}\\
    \midrule
    % \Fix{Versions (03.08)} & 234555 & 7.0.158 & 62.0b14 & 1.10.1 \\
    \Comment{
      Lembrar dos testes que os testes da propria engine falham:
      V8 0 
      JSC 2 
      Spidermonkey 58
    }
    \jsc{} & - & 9 & 10 & 58   \\
    \veight{} & 29 & - & 0 & 0  \\
%    \chakra{} & - & - & - & -  \\
    \smonkey{} & 217 & 106 & - & 278 \\
    Duktape & 0 & 4 & 4 & 1   \\
    \jerry{} & 23 & 25 & 22 & 23   \\
    JSI & 0 & 0 & 0 & 0   \\ 
   Tiny-js & 0 & 0 & 0 & 0  \\
    \midrule
   \textbf{total} & 270 & 145 & 36 & 361 \\
    \bottomrule 
  \end{tabular}
\end{table}

@@

% (\eg{},``New'', ``Rejected'', ``Confirmed'', ``Fixed'')

Table~\ref{fig:piecharts-transplantation} shows the distribution of
false and true positives. Considering false positives, ``Undefined
Behavior'' and ``Non-Standard Element'' were the most predominant
sources. Considering true positives, we found a reasonable number of
duplicate reports, but not enough high to justify attempting to
automate the detection of duplicates.
Table~\ref{tab:test-transplantation-bugs} lists all bugs we found with
test transplantation. The first column shows the identifier we
assigned to the bug\Comment{, column ``Date'' shows the date the bug
  was reported in the format ``m/dd'',}, column ``Engine'' shows the
affected engine, column ``Status'' shows the status of the bug report
at the time of the writing. The status string appears in bold face for
status ``Confirmed'' or higher, \ie{}, ``Assigned'' and ``Fixed''.
Column ``Url'' shows the URL (de-anonymized upon request) for the bug
report entry in the corresponding bug-tracking system, column
``Severity'' shows the severity level for confirmed bugs, and,
finally, column ``Suite'' shows the name of the engine that originated
the test. Note that bug reports \#4 and \#23 afected multiple
engines.

Considering severity levels, it is worth noting that \jsc{} uses five
levels~\cite{jsc-severity} whereas \chakra{}~\cite{chakra-severity}
and \smonkey{}~\cite{mozilla-severity} use only three\Mar{e v8?}. As
usual, the smallest the severity value the highest the severity of the
bug. We use a dash (``-'') in place of the severity level for the
cases where the bug report is pending confirmation.\Mar{por favor,
  corrija estes numeros *com cuidado*! se possivel, use macros.} Of
the \Fix{17} bugs we reported in this experiment, \Fix{9} were
promoted from the status ``New'' to ``Confirmed''. Of these, \Fix{8}
are severity-2 bugs.  Although we did not find any showstopper
critical bugs, most of the bugs are seemingly important as per the
categorization given by engineers. Analyzing the issue tracker of
\chakra, we found that severity-1 bugs are indeed rare. Considering
the bugs confirmed by developers, \chakra{} was the engine with the
highest number, \Fix{8} in total, with \Fix{1} bug fixed. Considering
the remaining engines, \veight{} developers confirmed \Fix{two} of the
\Fix{three} bug we reported, fixing \Fix{one}. Curiously, Google
engineers confirmed the report we issued in a few hours. We found that
development teams of other engines, specially \jsc\, took much longer
to analyze bug reports as can be observed in the \jsc\ stacked bar
from Figure~\ref{fig:stacked-engine}.

%% Overall, we found these results promising given that precision (\ie{},
%% the ratio of true positives over all reports) needs to take into
%% account the cost of inspecting the failure~\cite{harman-ohearn-2018};
%% it took a week for the developer to inspect the entire set of
%% failures. The precision for \jsc\ was \Fix{X\%} (\ie, XX/270), which
%% seems a low rate, but it took approximately \Fix{x} days to find
%% \Fix{y} real bugs on this engine. Section~\ref{sec:bugs} shows samples
%% of false and true positives.

\begin{center}
  \fbox{
    \begin{minipage}{8cm}
      \textit{Summary:}~Test transplantation is effective at finding
      functional bugs. Although the cost of classifying failures was
      non-negligible, the approach revealed several non-trivial bugs
      in widely popular engines.
      \end{minipage}
    }
\end{center}

@@
